---
title: "fabR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fabR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# fabR

<!-- badges: start -->
  [![R-CMD-check](https://github.com/GuiFabre/fabR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/GuiFabre/fabR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of fabR is to provide wrapper functions in the data cleaning and cleansing 
processes. These function help in messages and interaction with the user, keep track 
of information in pipelines, help in the wrangling, munging, assessement and visualization 
of data frame-like material.

## Installation

You can install the development version of fabR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("GuiFabre/fabR")
```

## Example

```{r setup}
library(fabR)
fabR_help()
```
