---
title: "fabR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fabR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  echo = TRUE)

```


# fabR

<!-- badges: start -->
  [![R-CMD-check](https://github.com/GuiFabre/fabR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/GuiFabre/fabR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of fabR is to provide wrapper functions in the data cleaning and 
cleansing processes. These function help in messages and interaction with the 
user, keep track of information in pipelines, help in the wrangling, munging, 
assessment and visualization of data frame-like material.

## Installation

You can install the package from CRAN, or the development version of fabR from
[GitHub](https://github.com/):

``` {r setup}
# To update the R package in your R environment you may first need to remove 
# it, and use the exit command quit() to terminate the current R session.

# To install the R package:
install.packages('fabR')
library(fabR) 

#if you need help with the package, please use:
fabR_help()

```
