---
title: "fabR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fabR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# fabR

<!-- badges: start -->
  [![R-CMD-check](https://github.com/GuiFabre/fabR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/GuiFabre/fabR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of fabR is to provide wrapper functions in the data cleaning and 
cleansing processes. These function help in messages and interaction with the 
user, keep track of information in pipelines, help in the wrangling, munging, 
assessment and visualization of data frame-like material.

## Installation

You can install the development version of fabR from [GitHub](https://github.com/) 
with:

``` {r setup}
install.packages("fabR",repos = "https://cloud.r-project.org/")

# install.package("devtools")
# devtools::install_github(repo = "https://github.com/guifabre/fabR", 
#  auth_token = "ghp_xxx",force = TRUE)

```

## Example

```{r}
library(fabR)
fabR_help()
```
